D3064R0: How to Avoid OOTA Without Really Trying

### 2024-02-24 ootavacuous.tex
Fix typo s/r1/r2/ in first paragraph of 8.1
Reported-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Computer systems are expected to continue increasing their use of
speculative execution.
Nevertheless, the main points of this paper will remain unaffected.
To see this, keep in mind that on real systems, observable effects
must eventually be committed, but that no effect can be committed
while any of the computations that determine the effect remain
speculative.
Furthermore, instructions take time to execute, even when executed
speculatively.
For example, in Listing~\ref{lst:Speculated Store and Non-Speculated Load},
suppose that the storage for \co{x} is located immediately before that
for \co{y[]}.
Suppose further that hardware speculation incorrectly guesses the value
of \co{i} to be -1, so that the speculated store of 42 on line~9 uses
the address of \co{x}.\footnote{
	Yes, \co{y[-1]} is UB, but the CPU neither knows
	nor cares, nor should it.}
Then line~11 can cause the value 42 to be loaded into \co{r1}, when
by the rules of the C++ abstract machine the value must instead be
either zero or one.

>>>>

Computer systems are expected to continue increasing their use of
speculative execution.
Nevertheless, the main points of this paper will remain unaffected.
To see this, keep in mind that on real systems, observable effects
must eventually be committed, but that no effect can be committed
while any of the computations that determine the effect remain
speculative.
Furthermore, instructions take time to execute, even when executed
speculatively.
For example, in Listing~\ref{lst:Speculated Store and Non-Speculated Load},
suppose that the storage for \co{x} is located immediately before that
for \co{y[]}.
Suppose further that hardware speculation incorrectly guesses the value
of \co{i} to be -1, so that the speculated store of 42 on line~9 uses
the address of \co{x}.\footnote{
	Yes, \co{y[-1]} is UB, but the CPU neither knows
	nor cares, nor should it.}
Then line~11 can cause the value 42 to be loaded into \co{r2},
thus satisfying the \co{exists} clause on line~20, when
by the rules of the C++ abstract machine the value must instead be
either zero or one.
